### 2020-05-07 README.Rmd
basic pkgdown structure

---
output:
  md_document:
    variant: markdown_github
---

@@

```{r, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/figures/",
  dev = "png",
  dpi = 150,
  fig.asp = 0.8,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center"
)
```

<img src="inst/figures/logo.png" width = 200 alt="dataaimsr Logo"/>

@@

If the environment variable `AIMS_DATA_PLATFORM_API_KEY` is stored in the user's `.Renviron` file then that will be loaded and used automatically.  In that case the users `.Renviron` file might look like:

@@

System     | .Renviron file locations
-----------|-------------------------
MS Windows | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
Linux      | `/home/<username>/.Renviron`

@@

```
devtools::install_git("https://github.com/AIMS/data-platform-r")
```

@@

Detailed Example
----------------

[A more detailed example of the R package usage on the weather dataset page.](10.25845/5c09bf93f315d/example-1.nb.html)  This is an [RStudio](https://www.rstudio.com/) Notebook and can be used interactively from [RStudio](https://www.rstudio.com/).  __Note that you need to have an AIMS Data Platform API Key available to run this detailed example.__

>>>>

---
output: github_document
---

@@

```{r, include = FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>

@@

If the environment variable `AIMS_DATAPLATFORM_API_KEY` is stored in the user's `.Renviron` file then that will be loaded and used automatically.  In that case the users `.Renviron` file might look like:

@@

System        | .Renviron file locations
--------------|-------------------------
MS Windows    | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
Linux / MacOs | `/home/<username>/.Renviron`

@@

```
devtools::install_github("https://github.com/AIMS/data-platform-r")
```

@@

Further Information
----------------
